Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-04 ch04-lrmhinf/paper.tex
Add guideline to CH04

  \begin{itemize}
    \item \TODO{add section from Benchmark paper}
  \end{itemize}
\newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
\newcommand{\dampingValue}{\ensuremath{0.025}}
\newcommand{\TsValue}{\ensuremath{1 \unit{s}}}

@@

We simulate the system \eqref{eq:lrmhinf:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:lrmhinf:LPMHinf}.
The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:lrmhinf:MC-run-length}.

@@

>>>>

  % \begin{itemize}
  %   \item \TODO{add section from Benchmark paper}
  % \end{itemize}
\newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
\newcommand{\dampingValue}{\ensuremath{0.025}}
\newcommand{\TsValue}{\ensuremath{1 \unit{s}}}

@@

We simulate the system \eqref{eq:lrmhinf:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:lrmhinf:LPMHinf}.
The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
This ensures that grid misalignment between the actual resonance frequency and the observed frequency grid is accounted for such that the worst-case estimate of the resonance is obtained.
These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:lrmhinf:MC-run-length}.

@@

\begin{guideline}[Measure $4$ to $5\timeconst$ to observe its peak value using the local models]
After $4$ to $5$ time constants of the dominant pole, the local models offer a reliable insight into the peak value of a transfer function when a sufficient \gls{SNR} of approximately $20\unit{dB}$ is available such that the \gls{LRM} can be used.
For purely \gls{FRF}-based estimates, on the other hand, the measurement only attains similar performance when measuring for $20\timeconst$.
\end{guideline}
